Flatiron cleaning

### 2021-10-06 Rmd/rdi analysis.Rmd
Update cleaning and add analysis

At this point, after cleaning the clinical data and excluding unfit patients, we have `r nrow(clinical_data)` patients.  
- exclude the patients who had surgery but we don't have a date  
- exclude patients whose histology is unknown  
- exclude patients who didn't survive 1 month

@@

therapy_line1 %>% 
  filter(linenumber == 2, treatment_sequence == "neo + surg + adj") %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linename) %>% 
  tbl_summary(sort = list(everything() ~ "frequency"))

@@

@@

@@

@@

>>>>

***
At this point, after cleaning the clinical data and excluding unfit patients, we have `r nrow(clinical_data)` patients.  
- exclude the patients who had surgery but we don't have a date  
- exclude patients whose histology is unknown  
- exclude patients who didn't survive 1 month

@@

therapy_line1 %>% 
  filter(linenumber_new == 2, treatment_sequence == "neo + surg + adj") %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linename) %>% 
  tbl_summary(sort = list(everything() ~ "frequency"))

@@

<br>
<br>

@@

# RDI calculation

RDI is calculated by drug so 1 for each Carboplatin, Cisplatin, Oxaloplatin, Paclitaxel, Paclitaxel protein bound, Docetaxel.

```{r}
Frontline <- Treatment %>% 
  # Calculate 1 RDI per drug per day, for whole Neoadjuvant and for first line of Adjuvant
    group_by(patientid, chemotherapy_type) %>% 
  mutate(linenumber_adj = dense_rank(linenumber_new)) %>%

  filter(chemotherapy_type == "Neoadjuvant" |
           (chemotherapy_type == "Adjuvant" &
              linenumber_adj == 1)) %>%

  mutate(relative_dose_intensity = case_when(
    chemotherapy_type == "Adjuvant" &
      linenumber_adj == 1                  ~ amount/expected_dose,
    chemotherapy_type == "Neoadjuvant"     ~ amount/expected_dose
  )) %>%

  # select(patientid,linenumber, linenumber_new, chemotherapy_type, drugname_type, drugname,
  #        relative_dose_intensity, linenumber_adj) %>%

  # Average RDI by taxel or platin by line (will NOT combine pacli-doce and cis-carbo-oxalo)
  group_by(patientid, chemotherapy_type, drugname_type) %>%
  mutate(mean_RDI_per_chemotype_drug = case_when(
    chemotherapy_type == "Adjuvant" &
      linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
    chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  )) %>% 
  ungroup() %>% 
  distinct(patientid, chemotherapy_type, drugname_type, .keep_all = TRUE)
```

```{r}
Frontline %>% distinct(patientid) %>% nrow()
```

## 2.Plots Clinical
<div class = "row">
<div class = "col-md-6">
```{r}
Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= bmi_cat))+
  geom_bar()+
  theme_minimal()+
  labs(title = "BMI category")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= histology))+
  geom_bar()+
  theme_minimal()+
  labs(title = "Histology")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= stagecat))+
  geom_bar()+
  theme_minimal()+
  labs(title = "Stage")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= agecat))+
  geom_bar()+
  theme_minimal()+
  labs(title = "Age cat")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= brca_germline))+
  geom_bar()+
  theme_minimal()+
  labs(title = "BRCA gernline")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= brca_tumor))+
  geom_bar()+
  theme_minimal()+
  labs(title = "BRCA tumor")+
  coord_flip()
```
</div>

<div class = "col-md-6">
```{r}
Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = bmi_cat))+
  geom_bar(position = "fill")+
  theme_minimal()+
  labs(title = "BMI category")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = histology))+
  geom_bar(position = "fill")+
  theme_minimal()+
  labs(title = "Histology")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = stagecat))+
  geom_bar(position = "fill")+
  theme_minimal()+
  labs(title = "Stage")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = agecat))+
  geom_bar(position = "fill")+
  theme_minimal()+
  labs(title = "Age cat")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = brca_germline))+
  geom_bar(position = "fill")+
  theme_minimal()+
  labs(title = "BRCA germline")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = brca_tumor))+
  geom_bar(position = "fill")+
  theme_minimal()+
  labs(title = "BRCA tumor")+
  coord_flip()
```
</div>
</div>

@@

## 3.Survivals by clinical

<span style="color:green">**Survival plots from date of diagnosis on the left and from date of treatment on the right**</span>

<div class = "row">
<div class = "col-md-6">
```{r clinical from dx, fig.height = 7}
# OS by raceeth
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ raceeth, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by tstage
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ stagecat, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by bmi_cat
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ bmi_cat, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by brca1_tumor
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_tumor, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by brca2_tumor
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_tumor, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by brca_tumor
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca_tumor, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by brca1_g
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_germline, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by brca2_g
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_germline, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by brca_g
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca_germline, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))
```
</div>

<div class = "col-md-6">
```{r clinical from first treatment, fig.height = 7}
# OS by raceeth
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ raceeth, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by tstage
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ stagecat, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by bmi_cat
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ bmi_cat, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by brca1_tumor
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca1_tumor, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by brca2_tumor
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca2_tumor, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by brca_tumor
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca_tumor, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))
# OS by brca1_g
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca1_germline, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by brca2_g
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca2_germline, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by brca_g
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca_germline, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))
```
</div>
</div>

<br>
<br>

@@

# II.Analysis Treatment

```{r Table 3}
# tbl1 <- 
  Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
  select(c(raceeth, #delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
           "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
           had_neo, had_adj,
           "chemotherapy_type", "therapy", "treatment_sequence"#, "relative_dose_intensity", "RDI_grp"
           )) %>% 
  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p(
    # test.args = all_tests("chisq.test") ~ list(workspace=2e9)
    ) %>% bold_p(t = .05)
# tbl2 <- Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
#   filter(exclude != "1") %>% 
#   select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
#            "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
#            "chemotherapy_type", "therapy", "treatment_sequence"#, "relative_dose_intensity", "RDI_grp"
#            )) %>% 
#   tbl_summary(by = raceeth, missing = "no") %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
# tbl_merge(list(tbl1, tbl2), tab_spanner = c("with unknown", "without unknown"))
```
<br>

## 2.Plots Treatment
<div class = "row">
<div class = "col-md-6">
```{r}
Frontline %>%
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= therapy))+
  geom_bar()+
  theme_minimal()+
  labs(title = "Frontline treatment")+
  coord_flip()

# Frontline %>% 
#   arrange(episodedate) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   group_by(chemotherapy_type) %>% 
#   summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
#   ggplot(aes(x= chemotherapy_type, y= percent, fill = chemotherapy_type))+
#   geom_bar(stat="identity")+
#   labs(x = "", title = "The first chemotherapy received by a patient Adjuvant for ~70% of the time") +
#   theme_minimal()+
#   guides(fill = FALSE) +
#   coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  # group_by(treatment_sequence) %>% 
  # summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
  ggplot(aes(x= treatment_sequence,
             # y= percent, 
             fill = treatment_sequence))+
  geom_bar(
    # stat="identity"
    )+
  labs(x = "", title = "The treatment_sequence") +
  theme_minimal()+
  guides(fill = FALSE) +
  coord_flip()

```
</div>

<div class = "col-md-6">
```{r}
Frontline %>%
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill= therapy))+
  geom_bar(position ="fill")+
  theme_minimal()+
  labs(title = "Frontline treatment")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  # group_by(treatment_sequence) %>% 
  # summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
  ggplot(aes(x= raceeth,
             # y= percent, 
             fill = treatment_sequence))+
  geom_bar(
    position ="fill"
    )+
  labs(x = "", title = "The treatment_sequence") +
  theme_minimal()+
  # guides(fill = FALSE) +
  coord_flip()

# Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
#   ggplot(aes(x= chemo))+
#   geom_bar()+
#   theme_minimal()+
#   coord_flip()
```
</div>
</div>

## 3.Survivals by treatment

<div class = "row">
<div class = "col-md-6">
```{r, fig.height = 7}
# OS by extentofdebulking
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ extentofdebulking, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 1))

# OS by residualdiseasestatus
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ residualdiseasestatus, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 1))

# OS by treatment_sequence
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ treatment_sequence, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 1))

# OS by therapy
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ therapy, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 1))
```
</div>
